Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-07-21 ms.tex
Fixed a typo

\section{Gamma Rays Emission from Cosmic Rays}
We decided to adopt a multifaceted approach to constrain the CR-to-thermal
pressure distribution in Coma with these upper limits. That includes (1) an
analytic model derived from cosmological hydrodynamical simulations of the
formation of galaxy clusters, (2) a simplified multi-frequency analytical
approach that assumes a constant CR-to-thermal energy density and a power-law
spectrum in momentum, and (3) an approach that uses the observed luminosity of
the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray
flux in the hadronic model -- independent of the magnetic field distribution.
This translates into a minimum CR pressure which, if challenged by tight
gamma-ray limits/detections, enables scrutinizing the hadronic interaction model
of the formation of giant radio halos.  Modelling the CR distribution through
different techniques enable to bracket our ignorance about the underlying plasma
physics that shape the CR distribution and hence reflect the Bayesian priors
that are imposed on the modelling \citep[see][for a
discussion]{article:PinzkePfrommerBergstrom}.

>>>>

\section{Gamma Ray Emission from Cosmic Rays}
We decided to adopt a multifaceted approach to constrain the CR-to-thermal
pressure distribution in Coma with these upper limits. That includes (1) an
analytic model derived from cosmological hydrodynamical simulations of the
formation of galaxy clusters, (2) a simplified multi-frequency analytical
approach that assumes a constant CR-to-thermal energy density and a power-law
spectrum in momentum, and (3) an approach that uses the observed luminosity of
the giant radio halo in Coma to place a lower limit on the expected $\gamma$-ray
flux in the hadronic model -- independent of the magnetic field distribution.
This translates into a minimum CR pressure which, if challenged by tight
gamma-ray limits/detections, enables scrutinizing the hadronic interaction model
of the formation of giant radio halos.  Modelling the CR distribution through
different techniques enable to bracket our ignorance about the underlying plasma
physics that shape the CR distribution and hence reflect the Bayesian priors
that are imposed on the modelling \citep[see][for a
discussion]{article:PinzkePfrommerBergstrom}.
